---
title: "Developing the method with Russian River steelhead"
output: 
  html_notebook:
    toc: true
---


## Packages and such
```{r}
library(tidyverse)
library( tidyInbredPermute)
```

## Input Data Files

Anne has been cranking on the Russian River steelhead data set and
has supplied me with some data files to get going on.

She provided me with three files, but it was the first two that
are going to be most important.  I have put those into `inst/extdata`
so that they will be available in mostly unmodified form in the package
(I did turn them into CSVs and I gzipped them.)  The files in this
repository are at:
```
./inst/extdata/RR_parentage_corrected-sexes_June27_2019.csv.gz
./inst/extdata/RR_steelhead_genotype_meta.csv.gz
```
And I have wrapped those up as data objects in the package:
`genos_and_meta` and `trios`.

Anne is going to get me some other files that tell us when the hatchery believes
each of the different fish was spawned (over multiple occasions).  But before then
I will get started.

She's given me that now, it is in:
```
./inst/extdata/RR_ID_Date_Sex.csv.gz
```

### Checking out the ID file

I just want to do a few quick counts to make sure that 
sex is consistent for those individuals, and to count
up how many individuals were spawned on different numbers of days.
```{r}
rrids <- read_csv("./inst/extdata/RR_steelhead_07-20_known_sexes.csv")

# get distribution of number of days spawned
rrids %>%
  count(indiv) %>%
  count(n)
```

if the fish return to spawn more than once, there are mulitiple dates listed in 'spawner_group', sepearted by a comma

Now, check the sex:
```{r}
rrids %>%
  group_by(indiv) %>%
  summarise(num_sexes = unique(new_sex)) %>%
  count(num_sexes)
```

there are 167 fish with unclear sexes, it is probably best to remove these fish from this analysis


```{r}
cleaner_rrids <- rrids %>% 
  filter(!is.na(new_sex))
  
cleaner_rrids %>% count(spawner_group)
#there are seven fish with unknown spawn dates (all from 2013), they are marked with a "?"
#there is one fish that was in this unknown spawn group and spawned a second time, this fish as a "?" followed by a real date
  
```
#what is the best way to display the muliple dates for spawning? as multiple columns? I can easily split the dates...
```{r}
spawn_col <- cleaner_rrids %>% 
  separate(spawner_group, c("spawn_1", "spawn_2", "spawn_3"), sep = ",") %>% 
  mutate(num_spawn = case_when(!is.na(spawn_3) ~ 3,
                               !is.na(spawn_2) & is.na(spawn_3) ~ 2, 
                               is.na(spawn_2) & is.na(spawn_3) ~ 1))
spawn_col %>%   count(num_spawn)

spawn_rows <- spawn_col %>% 
  pivot_longer(cols = starts_with("spawn_"), names_to = "spawn_event", values_to = "spawn_date") %>% 
  filter(!is.na(spawn_date))
```



## Computing pairwise Rxy

Clearly we don't want to compute this for all possible pairs over the 12 years, or
whatever it is.  That just would make no sense.  But, we probably don't want to
compute it just for every spawning day ('cuz I think there is program overhead
in calling related...**Turns out, no! You definitely want to compute Rxy by spawn date. See below...**).  So, maybe we just do pairs of all individuals that are known
to have been spawned in a certain year.

I can test that out, and pairs that happen to be in two different years will be there
to make sure we are getting the same results with different individuals (confirming that
I am inputting the allele freqs in correctly).

### Read in the data

I am going to read in data for all of the NMFS_DNA_IDs and get it set up for use
by the related package.
```{r}
genos <- read_csv("./inst/extdata/RR_2007-2020_wide_genos_rm7_before_msa.csv") %>% 
  rename(indiv = "NMFS_DNA_ID")
genos_and_meta <- left_join(spawn_rows, genos, by = "indiv")
```


```{r}
# write to a file
genos_and_meta %>%
  select(indiv, Omy_AldA:`SH127510-920_1`) %>%
  write.table(sep = "\t", file = "temp.tsv", row.names = FALSE, col.names = FALSE, quote = FALSE)

# then read it in
rdat <- related::readgenotypedata("temp.tsv")
```

Now, we can run related on any subset of those (but keeping the same allele frequencies)
by just swapping out the gdata portion.
```{r}
# first 10 indivs
rel1 <- related::coancestry(rdat$gdata[1:10,], quellergt=1, allele.freqs = rdat$freqs)$relatedness %>%
  as_tibble() %>%
  select(ind1.id, ind2.id, quellergt)

# first 5 indivs
rel2 <- related::coancestry(rdat$gdata[1:5,], quellergt=1, allele.freqs = rdat$freqs)$relatedness %>%
  as_tibble() %>%
  select(ind1.id, ind2.id, quellergt)

# note that you get the same result for the shared individuals.
```

OK, so, if I wanted to just do the individuals spawned in 2013, for example, it would look like this:
```{r, eval=FALSE}
ids2013 <- genos_and_meta %>%
  select(indiv, year) %>%
  filter(year == 2013) %>%
  pull(indiv)

geno2013 <- rdat$gdata %>%
  filter(V1 %in% ids2013)

rxy2013 <- related::coancestry(geno2013, quellergt=1, allele.freqs = rdat$freqs)$relatedness %>%
  as_tibble() %>%
  select(ind1.id, ind2.id, quellergt)
```
That takes about two minutes.  But it gets the job done.

#how about 2020, is my genos_and_meta file working correctly?
```{r, eval=FALSE}
ids2020 <- genos_and_meta %>%
  select(indiv, year) %>%
  filter(year == 2020) %>%
  pull(indiv)

geno2020 <- rdat$gdata %>%
  filter(V1 %in% ids2020)

rxy2020 <- related::coancestry(geno2020, quellergt=1, allele.freqs = rdat$freqs)$relatedness %>%
  as_tibble() %>%
  select(ind1.id, ind2.id, quellergt)

```

yes it worked

So, using the years in `ids_sex_date` I will get rxys for all fish spawned in a
particular years...for all the years.  And then I will bind those into
a single data frame of all the pairs that I think I am going to need.  
That will include pairs formed from all fish reported to spawn in a particular year.  
I can save that whole object (three columns, ind1, ind2, quellergt). And I might need 
to switch things up so that the pairs are recognizable in both directions, and maybe
do a little other filtering.  But that will be what we consider to be the input
that we will need.

Here we go....

## Computing all the Rxys that we might possibly need

This is a job for purrr and friends.

Note that there is a wrinkle first.  We don't have genetic data for every fish in id_sex_date,
and if we don't have that, we can't do anything with it. So, we are going to condition all of this
on fish that we have genetic data for.  Let's figure those out:
```{r}
setdiff(cleaner_rrids$indiv, rdat$gdata$V1)
```
OK, every NMFS_DNA_ID in `id_sex_date` has an entry in the genotype data.

But what about the other way around?
```{r}
setdiff(rdat$gdata$V1, cleaner_rrids$indiv)
```
There are a few there, but that shouldn't cause any problems.


So, here is a function that takes a data frame called data and returns
all possible rxys between the IDS in that data frame.

```{r}
get_rxys <- function(data) {
  d <- semi_join(rdat$gdata, data, by = c("V1" = "indiv"))
  rxy1 <- related::coancestry(d, quellergt=1, allele.freqs = rdat$freqs)$relatedness %>%
    as_tibble() %>%
    select(ind1.id, ind2.id, quellergt) %>%
    rename(ind1 = ind1.id, ind2 = ind2.id)
  rxy2 <- rxy1[, c(2,1,3)] %>%
    set_names(c("ind1", "ind2", "quellergt"))
  
  bind_rows(rxy1, rxy2)
}
```


## Wait! Try doing just the pairs you need for each day

Looking at the result here, we see that it is 514 Mb.  Almost half a gig.  That is way
too big!  So, maybe it would make more sense to just compile up all the pairs
for each day.  Given that we don't see the same individual on too many different days,
that should be fine...



But, for now, we will compute the rxys between pairs on a daily basis.  Pretty mellow
given the machinery that we have prepared above. Note that we may as well filter out any days
that we don't have returning trios for.  This might toss out some of the dates that list one spawner.
#AKB resuming here to try by date
#Seperated by hatcheries -- Warm springs and coyote valley
```{r}
library(lubridate)
trios <- read_csv("./inst/extdata/RR_pedigree_07-20_known_sexes_and_dates.csv")
trios %>% count(parent_sg)
trios %>% count(ma_hatchery)

trios_to_use_WS <- trios %>%
  filter(parent_sg != "NULL", 
         parent_sg != "?" , 
         parent_sg != 'c("02/16/12", "02/10/12")', 
         parent_sg != 'c("03/03/11", "02/26/11")') %>%
  filter(new_ma_sex == "Female", new_pa_sex == "Male") %>% 
  filter(ma_hatchery == "Warm_Springs") %>% 
  select(SpawnYear, pa, ma, parent_sg) %>%
  mutate(spawn_date = mdy(parent_sg))

trios_to_use_CV <- trios %>%
  filter(parent_sg != "NULL", 
         parent_sg != "?" , 
         parent_sg != 'c("02/16/12", "02/10/12")', 
         parent_sg != 'c("03/03/11", "02/26/11")') %>%
  filter(new_ma_sex == "Female", new_pa_sex == "Male") %>% 
  filter(ma_hatchery == "Coyote_Valley") %>% 
  select(SpawnYear, pa, ma, parent_sg) %>%
  mutate(spawn_date = mdy(parent_sg))
  
  #here! I need to make two data files, one for WS and one for CV

day_fish_WS <- spawn_rows %>%
  mutate(spawn_date = mdy(spawn_date)) %>%
  group_by(spawn_date) %>%
  nest() %>%
  semi_join(trios_to_use_WS, by = "spawn_date") %>%
  arrange(spawn_date) %>%
  mutate(num_fish = map_int(data, nrow))

day_fish_CV <- spawn_rows %>%
  mutate(spawn_date = mdy(spawn_date)) %>%
  group_by(spawn_date) %>%
  nest() %>%
  semi_join(trios_to_use_CV, by = "spawn_date") %>%
  arrange(spawn_date) %>%
  mutate(num_fish = map_int(data, nrow))

day_fish_WS
day_fish_CV
```

Reassuringly, there are not any days with 1 spawner that produced trios....

Anyway, now that we have 171 different days, from which some trios were
identified, we can compute the rxys for all the possible parents on those days.
```{r, eval=FALSE}
rxys_in_days_WS <- day_fish_WS %>%
  mutate(pairs = map(data, get_rxys))

rxys_in_days_CV <- day_fish_CV %>%
  mutate(pairs = map(data, get_rxys))
```

Don't evaluate that one in a notebook!  related writes so much to the console that it gets f*&^#d up. 
That dude is only 30 Mb, and took a lot less time to calculate.  That is clearly the way to go.

I'll chuck the `rxys_in_years` from the package, and I will save rxys_in_days to it.


## Add the trios in there

Clearly the thing to do now is to add into there a list column that has all the
trios that were assigned to particular spawn dates:
```{r}
nested_trios_WS <- trios_to_use_WS %>%
  group_by(spawn_date) %>%
  nest() %>%
  arrange(spawn_date) %>%
  mutate(n_trios = map_int(data, nrow),
         n_dads = map_int(data, function(x) n_distinct(x$pa)),
         n_moms = map_int(data, function(x) n_distinct(x$ma))) %>%
  rename(trios = data)

nested_trios_CV <- trios_to_use_CV %>%
  group_by(spawn_date) %>%
  nest() %>%
  arrange(spawn_date) %>%
  mutate(n_trios = map_int(data, nrow),
         n_dads = map_int(data, function(x) n_distinct(x$pa)),
         n_moms = map_int(data, function(x) n_distinct(x$ma))) %>%
  rename(trios = data)

interm1_WS <- rxys_in_days_WS %>%
  rename(spawners = data,
         rxy_pairs = pairs) %>%
  left_join(nested_trios_WS, by = "spawn_date")

interm1_CV <- rxys_in_days_CV %>%
  rename(spawners = data,
         rxy_pairs = pairs) %>%
  left_join(nested_trios_CV, by = "spawn_date")

interm1_WS
interm1_CV
```

OK, `interm1` basically has everything that we need to operate on each spawn
day and do what we need to do.

My basic feeling about this now is that we should mirror the distribution
of observed family sizes and things, too.  In other words, we  should basically
randomly map spawning males to observed fathers in trios, and spawning females
to observed mothers in trios, and compute the distribution of rxy values that way.

That will preserve the (extra) variance that is due to the fact that we don't have a random
number of individuals from each pair, etc. So, I just need to figure out how to
do that efficiently.  




## Doing the permutations and extracting Rxy

So, what we want to do is get the observed rxy values for all of the trio pairs found.  Let's make a function
for that first.

Here is a function for extracting the actual Rxy:
```{r}
#' @param tdf trio data frame.  An element of the trios list column
#' @param rxyp rxy_pairs data frame.  An element of the rxy_pairs list column
extract_observed_rxy <- function(tdf, rxyp) {
  left_join(tdf, rxyp, by = c("pa" = "ind1", "ma" = "ind2"))
}
```

And how about a function for extracting Rxys when random males or females are
assigned to those Pa_IDs and Ma_IDs.  I have a way to do this efficiently, I do
believe.  We do it all with a few joins in series.
```{r}
#' @param tdf trio data frame.  An element of the trios list column
#' @param rxyp rxy_pairs data frame.  An element of the rxy_pairs list column
#' @param spaw spawners data frame.  An element of the spawners list column
#' @param nperm number of permutations to consider
extract_permuted_rxy <- function(tdf, rxyp, spaw, nperm = 100) {
  
  # vectors of males and females observed in trios
  obs_males <- unique(tdf$pa)
  obs_females <- unique(tdf$ma)
  
  # vectors of the males and females that were actually spawned on that day
  smales <- spaw %>%
    filter(new_sex == "Male") %>%
    pull(indiv)
  
  sfemales <- spaw %>%
    filter(new_sex == "Female") %>%
    pull(indiv)
  
  # tibbles of permuted males (females) assigned to observed males (females)
  pmales <- tibble(
    perm = rep(1:nperm, each = length(obs_males)),
    pa = rep(obs_males, times = nperm),
    ind1 = unlist(lapply(1:nperm, function(i) sample(x = smales, size = length(obs_males), replace = FALSE)))
  )
  
  pfemales <- tibble(
    perm = rep(1:nperm, each = length(obs_females)),
    ma = rep(obs_females, times = nperm),
    ind2 = unlist(lapply(1:nperm, function(i) sample(x = sfemales, size = length(obs_females), replace = FALSE)))
  )
  
  # now we join that with the trios and then extract the pairwise rxy values for those.
  # we will toss all the columns that have the Pa_ID and Ma_ID there for each permutation,
  # but those might be useful later.  This is where we should come back to get it if we need it
  # later. In fact, I do that (by commenting a few lines out) here so that I will be able to assess things later.
  tdf %>% 
    left_join(pmales, by = "pa") %>%
    left_join(pfemales, by = c("perm", "ma")) %>%
    arrange(perm, pa, ma) %>%
    left_join(rxyp, by = c("ind1", "ind2")) # %>%
    # select(perm, quellergt)
}
```


So, now we just need to use those...
```{r}
#Warm Springs
set.seed(100)  # for reproducibility
permy_results_WS <- interm1_WS %>%
  mutate(obs_rxy = map2(.x = trios, .y = rxy_pairs, .f = extract_observed_rxy),
         perm_rxy = pmap(.l = list(trios, rxy_pairs, spawners), .f = extract_permuted_rxy, nperm = 100)
         )

#Coyote Valley
set.seed(100)  # for reproducibility
permy_results_CV <- interm1_CV %>%
  mutate(obs_rxy = map2(.x = trios, .y = rxy_pairs, .f = extract_observed_rxy),
         perm_rxy = pmap(.l = list(trios, rxy_pairs, spawners), .f = extract_permuted_rxy, nperm = 100)
         )
```

```{r}
permy_results_WS$obs_rxy
```


## Look at the results

Quick look at means:
```{r}
##Warm springs
obs_means_WS <- permy_results_WS %>%
  mutate(obs_mean = map_dbl(obs_rxy, function(x) mean(x$quellergt))) %>%
  select(spawn_date, obs_mean)

perm_means_WS <- permy_results_WS %>%
  mutate(perm_means = map(perm_rxy, function(x) x %>% group_by(perm) %>% summarise(perm_mean = mean(quellergt)))) %>%
  select(spawn_date, perm_means) %>%
  unnest(perm_means)

# now, we can join those on spawn date:
the_means_WS <- obs_means_WS %>%
  left_join(perm_means_WS, by = "spawn_date") %>%
  group_by(spawn_date) %>%
  mutate(perm_means_mean = mean(perm_mean))

##Coyote Valley
obs_means_CV <- permy_results_CV %>%
  mutate(obs_mean = map_dbl(obs_rxy, function(x) mean(x$quellergt))) %>%
  select(spawn_date, obs_mean)

perm_means_CV <- permy_results_CV %>%
  mutate(perm_means = map(perm_rxy, function(x) x %>% group_by(perm) %>% summarise(perm_mean = mean(quellergt)))) %>%
  select(spawn_date, perm_means) %>%
  unnest(perm_means)

# now, we can join those on spawn date:
the_means_CV <- obs_means_CV %>%
  left_join(perm_means_CV, by = "spawn_date") %>%
  group_by(spawn_date) %>%
  mutate(perm_means_mean = mean(perm_mean))

```


Now, we can plot those means:
```{r}
#warm springs
ggplot(the_means_WS, aes(x = perm_means_mean, y = obs_mean)) + 
  geom_point(colour = "blue") +
  geom_abline(intercept = 0, slope = 1)
```
```{r}
#coyote valley
ggplot(the_means_CV, aes(x = perm_means_mean, y = obs_mean)) + 
  geom_point(colour = "blue") +
  geom_abline(intercept = 0, slope = 1)
```

That isn't super compelling.  So, there does not seem to be a super noticeable effect on means.

### So, let's look at distributions of value across all days

```{r}
#Warm springs
obs_dsn_WS <- permy_results_WS %>%
  select(spawn_date, obs_rxy) %>%
  unnest(obs_rxy) %>%
  select(spawn_date, quellergt)

permy_dsn_WS <-  permy_results_WS %>%
  select(spawn_date, perm_rxy) %>%
  unnest(perm_rxy)

the_dsns_WS <- bind_rows(list(observed = obs_dsn_WS, permuted = permy_dsn_WS),
                      .id = "type")
  
histo <- ggplot(the_dsns_WS, aes(x = quellergt, fill = type)) + 
  geom_histogram(aes(y = ..density..),
                 position = position_identity(),
                 alpha = 0.3)+
  ggtitle("Warm Springs")

# let's save that big so we can zoom in on it
dir.create("outputs", showWarnings = FALSE)
ggsave(histo, filename = "outputs/permy_histo_compare_WS.pdf", width = 10, height = 6)
histo 
```
```{r}
#Coyote valley
obs_dsn_CV <- permy_results_CV %>%
  select(spawn_date, obs_rxy) %>%
  unnest(obs_rxy) %>%
  select(spawn_date, quellergt)

permy_dsn_CV <-  permy_results_CV %>%
  select(spawn_date, perm_rxy) %>%
  unnest(perm_rxy)

the_dsns_CV <- bind_rows(list(observed = obs_dsn_CV, permuted = permy_dsn_CV),
                      .id = "type")
  
histo <- ggplot(the_dsns_CV, aes(x = quellergt, fill = type)) + 
  geom_histogram(aes(y = ..density..),
                 position = position_identity(),
                 alpha = 0.3)+
  ggtitle("Coyote Valley")

# let's save that big so we can zoom in on it
dir.create("outputs", showWarnings = FALSE)
ggsave(histo, filename = "outputs/permy_histo_compare_CV.pdf", width = 10, height = 6)
histo 
```


That is not looking like a super big difference either.  Interesting.

How about if we compare the empiricial CDFs:
```{r}
#warm springs
ggplot(the_dsns_WS, aes(x = quellergt, colour = type)) +
  stat_ecdf()+
  ggtitle("Warm Springs")

#coyote valley
ggplot(the_dsns_CV, aes(x = quellergt, colour = type)) +
  stat_ecdf()+
  ggtitle("Coyote Valley")
```

That is also pretty much the same.  

OK, this is interesting and somewhat unexpected...

I am going to check over the results to make sure that things appear to be done correctly.

## Testing/Checking

One test that I can do is make sure that males are assigned Pa_IDs and females
to Ma_IDs uniformly on each day over the permutations.  That will be good
to verify.  I should be able to do that by just analyzing the results.
```{r}
dsn_of_male_replacements <- function(pr) {
  males <- pr %>%
    group_by(perm, pa, ind1) %>%
    tally() %>%
    select(-n) %>%
    group_by(pa, ind1) %>%
    tally()
  
  ggplot(males, aes(x = ind1, y = n)) + geom_col() + facet_wrap(~ pa)
}

dsn_of_female_replacements <- function(pr) {
  females <- pr %>%
    group_by(perm, ma, ind2) %>%
    tally() %>%
    select(-n) %>%
    group_by(ma, ind2) %>%
    tally()
  
  ggplot(females, aes(x = ind2, y = n)) + geom_col() + facet_wrap(~ ma)
}
```

Now, with those functions we can spot check a few days:
```{r}
# choose 2011-03-03
PR1 <- permy_results_CV %>%
  filter(spawn_date == ymd("2011-03-03")) %>%
  pull(perm_rxy)

dsn_of_male_replacements(PR1[[1]])
```
 
That is looking pretty darn uniform.  Let's look at the same for the females:
```{r}
dsn_of_female_replacements(PR1[[1]])
```
 
Yep, once again, that is looking nicely uniform.
 
Now, let's take a look at the observed vs permuted pairwise rxy values on this
day across all the observed pairs to make sure that things look all right.
We will spot check that one day.
```{r}
PRT <- permy_results_WS %>%
  filter(spawn_date == ymd("2011-03-03"))

joined <- left_join(PRT$obs_rxy[[1]], PRT$perm_rxy[[1]], by = c("pa", "ma")) %>%
  rename(Obs_rxy = quellergt.x,
         Perm_rxy = quellergt.y)

ggplot(joined, aes(x = Obs_rxy, y = Perm_rxy)) +
  geom_point(alpha = 0.05, colour = "blue")
```


That all looks great.  So, I think there are no issues/problems/errors in what I have done.

## Look at number of rxy > 0.5

So, the one thing that we can say is appears, is that the permutations have some values 
above 0.5, while we don't observe many (if any at all) of those in the observed data.
But is that significantly fewer?  How many can we expect to have seen?  Recall that
we did 100 permutatations.  So the expected number of such pairs is the numbers we've
seen in the permutations divided by 100.  Let's check it out.
```{r}
# here is how many we would have expected at rxy > 0.5 from the
# permutations
sum(permy_dsn_WS$quellergt > 0.5) / 100
sum(permy_dsn_CV$quellergt > 0.5) / 100
```
which is a fraction of:
```{r}
(sum(permy_dsn_WS$quellergt > 0.5) / 100) / nrow(obs_dsn_WS)
(sum(permy_dsn_CV$quellergt > 0.5) / 100) / nrow(obs_dsn_CV)
```
which means that we are only expected 0.14% of the offspring under random mating
would have inbreeding greater than 0.5.

How many did we observe?
```{r}
obs_dsn_WS %>% filter(quellergt > 0.5) %>% nrow()
sum(obs_dsn_WS$quellergt > 0.5) # not working
obs_dsn_CV %>% filter(quellergt > 0.5) %>% nrow()
obs_dsn_CV %>% arrange(desc(quellergt))
obs_dsn_WS %>% arrange(desc(quellergt))
```
So, we saw two of those for WS, zero for CV.

How about over 0.4?
```{r}
sum(obs_dsn_CV$quellergt > 0.4) #notworking
obs_dsn_WS %>% filter(quellergt > 0.4) %>% nrow()
obs_dsn_CV %>% filter(quellergt > 0.4) %>% nrow()
```
11 for WS, 4 for CV
So, the effect of inbreeding on survival in this hatchery seems awfully low.  Very interesting.

Let's do some calculations from the Binomial distribution:
```{r}
RP <- rbinom(n = 1e5, size = nrow(obs_dsn_WS), prob = 0.00107904)
hist(RP)

RP_CV <- rbinom(n = 1e5, size = nrow(obs_dsn_CV), prob =0.001399063)
hist(RP)
```
So, how unusual would it be to find only 1:
```{r}
mean(RP <= 1)

mean(RP_CV <= 1)
```
Pretty small probability.  So, this might be significant.

### Assessing distribution over perms of the number of rxy > 0.5

We can do better than that by looking at how many offspring by inbreeding
greater than 0.5 in each of the perms and checking out the distribution there:
```{r}
num_over0.5 <- permy_dsn_WS %>%
  group_by(perm) %>%
  summarise(n_over = sum(quellergt > 0.5))

hist(num_over0.5$n_over)

num_over0.5_CV <- permy_dsn_CV %>%
  group_by(perm) %>%
  summarise(n_over = sum(quellergt > 0.5))

hist(num_over0.5_CV$n_over)
```

And how many of the 100 permutations have 1 or fewer with rxy > 0.5?
```{r}
sum(num_over0.5$n_over <= 1)

sum(num_over0.5_CV$n_over <= 1)
```

So, three out of 100 times.  Giving a permutation based p-value of 0.03 
11 out of 100 gives a permutation based pvalue of 0.11

